---
title: "Homework 1"
author: "Qianhui Xu"
output: github_document
---


```{r, include = FALSE }
library(tidyverse)
```

# Problem 1

## Create a data frame with the specified elements. 

```{r problem_one}
prob1_df = 
  tibble(
   samp_numeric = rnorm(10),
   samp_logical = samp_numeric > 0,
   char_vec = c("A", "A", "B", "B", "A", "C", "B", "C", "C", "A"),
  factor_vec = factor(c("high", "high", "mid", "mid", "high", "low", "mid", "low", "low", "high"))
  )
```

## Means
```{r means_var}
mean(pull(prob1_df,samp_numeric))
mean(pull(prob1_df, samp_logical))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

## What works and what doesn't?

Take the mean of each variable in my data frame.I found that we could obtain the means for numeric and logical variables. However, we could not obtain the means for character variable, and factor variable. 

#Convert

```{r prob_convert, eval = FALSE}
as.numeric(pull(prob1_df, samp_logical))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

## What happens and why?

The logical variable and factor variable  can be converted to numeric variables. It' because the logical variables could be stored as 0 (FALSE) and 1 (TRUE). Therefore,  the "FALSE" could be converted to 0  and  "TRUE" could be converted to 1. 

For factor variables, the elements could be converted to the numeric codes that correspond to the factor levels.(in our sample, we have 3 levels) Because factor vector contains and stores a set of numeric codes with character-valued levels. 

However, the character variable could not be converted to numeric variable.Because character variable contains characters, which could not be converted to numeric values.

Yes, this could help me to explain what happens when I try to make the mean. Because numeric and logical variables are stored as numeric values.We could therefore obtain their mean values. However, the factor variables could be converted to numeric variables but after the convertion, we could not obtain the mean value before convertion. The character variables contains characters and we could not obtain the mean from it.


## Problem1,second code chunk

```{r problem_one_second_chunk}
as.numeric(pull(prob1_df, samp_logical)) * pull(prob1_df, samp_numeric)
as.factor(pull(prob1_df, samp_logical)) * pull(prob1_df, samp_numeric)
as.numeric(as.factor(pull(prob1_df, samp_logical))) * pull(prob1_df, samp_numeric)
```

# Problem 2

```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```
## Discription of the dataset

The variable names are: `r names(penguins)`

The median of the body mass is `r median(pull(penguins, body_mass_g), na.rm = TRUE)`, the range for bill depth is`r  range(pull(penguins, bill_depth_mm), na.rm = TRUE)`.the range for bill length is`r  range(pull(penguins, bill_length_mm), na.rm = TRUE)`.
The penguins are from `r nlevels(pull(penguins, island))` islands. The names of each island are `r levels(pull(penguins, island))`.There are  `r nlevels(pull(penguins, species))` penguin species. The names of each species are `r levels(pull(penguins, species))`.


There are `r nrow(penguins)`rows and `r ncol(penguins)`columns in this dataset, and The size of the dataset is `r nrow(penguins)*ncol(penguins)`.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

## Scatterplot and save
```{r scatterplot_penguins}

#create scatterplot and related labels

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + ggtitle("Scatter plot")

#save and export the scatter plot

ggsave("scatterplot_penguins.pdf", height = 4, width = 4) 

```










