---
title: "Homework 1"
author: "Qianhui Xu"
output: github_document
---


```{r, include = FALSE }
library(tidyverse)
```

###Problem 1

#Create a data frame with the specified elements. 

```{r problem_one}
prob1_df = 
  tibble(
   samp_numeric = rnorm(10, sd = 1),
   samp_logical = samp_numeric > 0,
   char_vec = c("A", "A", "B", "B", "A", "C", "B", "C", "C", "A"),
  factor_vec = factor(c("high", "high", "mid", "mid", "high", "low", "mid", "low", "low", "high"))
  )
```

#Means
```{r means_var}
mean(pull(prob1_df,samp_numeric))
mean(pull(prob1_df, samp_logical))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

#What works and what doesn't?

Take the mean of each variable in my data frame.I found that we could obtain the means for numeric vector and logical vector. However, we could not obtain the means for character vector, and factor vector. 

#Convert

```{r prob_convert, eval = FALSE}
as.numeric(pull(prob1_df, samp_logical))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

#What happens and why?

The logical variable and factor variable  can be converted to numeric variables. It' because the logical variables could be stored as 0 (FALSE) and 1 (TRUE). Therefore,  the "FALSE" could be converted to 0  and  "TRUE" could be converted to 1. 
For factor variables, the elements could be converted to the numeric codes that correspond to the factor levels. Because factor vector contains and stores a set of numeric codes with character-valued levels. 
However, the character variable could not be converted to numeric variable.Because character variable contains string values, which could not be converted to numeric values.

#Problem1,second code chunk

```{r problem_one_second_chunk}
as.numeric(pull(prob1_df, samp_logical)) * pull(prob1_df, samp_numeric)
as.factor(pull(prob1_df, samp_logical)) * pull(prob1_df, samp_numeric)
as.numeric(as.factor(pull(prob1_df, samp_logical))) * pull(prob1_df, samp_numeric)
```

###Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```
#discription of the dataset

The discription of the data could be seen in `r summary(penguins)`, and the variable names are: `r names(penguins)`.  

There are `r nrow(penguins)` and `r ncol(penguins)`columns in this dataset. As we can see, there are 8 variables.

The size of the dataset is `r nrow(penguins)`*`r ncol(penguins)`.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm.

#scatterplot and save
```{r scatterplot_penguins}

#create scatterplot and related labels

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + ggtitle("Scatter plot")

#save and export the scatter plot

ggsave("scatterplot_penguins.pdf", height = 4, width = 4) 

```










